A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
writing construction for M

\paragraph{Recursive construction for $M$} Now we turn to the construction for the core algorithm $M$ for the correctness of the algorithm above.

>>>>

\paragraph{Recursive construction for $M$} Now we turn to the construction for the core algorithm $M$ for the correctness of the algorithm above. Steinberg designed several mutually disjoint reduction procedures that are applied when specific geometric properties are observed in input instances. Specifically, the input is categorized to fall into one of four classes $C_0, C_1, C_2, C_3$, where corresponding procedures $P_0,P_1, P_2,P_3$ would either solve $L$ or reduce to problems of smaller sizes.
\par The four classes are designed as below.\\
(C0) $w_M\leq \frac{w}{2}, h_M\leq\frac{h}{2},$ and for some index $i\in[1,n]$ we have $A-\frac{1}{4}wh\leq s_i$ \\
(C1) $w_M\geq \frac{w}{2}$ \\
(C2) $w_M\leq \frac{w}{2}, h_M\leq\frac{h}{2}$, and there exists two different indices $i$ and $k$ such that $w_i\geq \frac{w}{4}, w_k\geq\frac{w}{4}, h_i\geq\frac{w}{4}, h_k\geq\frac{h}{4}, 2(A-a_i-a_k)\leq (w-\max(w_i, w_k))h$ \\
(C3) $w_M\leq\frac{w}{2}, h_M\leq\frac{h}{2}, n>1$, and for some index $m\in[1,n)$ we have $A-\frac{1}{4}wh\leq\sum_{i=1}^{m}s_i\leq\frac{3}{8}wh$ and $w_{m+1}\leq\frac{w}{4}$
